A comparison of design-based and model-based approaches for spatial data.

### 2021-08-12 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
added a couple more discussion points.

* Pros of Model-Based (items we are not exploring): covariate inference, more efficient small-area estimation, model selection?

>>>>

* Pros of Model-Based (items we are not exploring): covariate inference, more efficient small-area estimation, model selection?, estimated spatial parameters to better understand spatial structure, site-by-site predictions/prediction map

### 2021-08-12 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.tex
added a couple more discussion points.

\begin{itemize}
\item
  Pros of Design-Based (items we are not exploring): computationally
  efficient, few assumptions, more naturally handles binary data,
\item
  Pros of Model-Based (items we are not exploring): covariate inference,
  more efficient small-area estimation, model selection?
\end{itemize}

>>>>

\begin{itemize}
\item
  Pros of Design-Based (items we are not exploring): computationally
  efficient, few assumptions, more naturally handles binary data,
\item
  Pros of Model-Based (items we are not exploring): covariate inference,
  more efficient small-area estimation, model selection?, estimated
  spatial parameters to better understand spatial structure,
  site-by-site predictions/prediction map
\end{itemize}
